extracting mean profiles

### 2016-04-08 mean-profiles.Rmd
getting the twist rate calculated from median

br115 <- "~/CSAFE/Bullets/Hamby252_3DX3P1of2/Br1 Bullet 2-1.x3p"
im115 <- fortify_x3p(read.x3pplus(br115))
qplot(y, x, fill=value, data=im115, geom="tile")
ggsave(file="im115.pdf")

>>>>

br115 <- "~/CSAFE/Bullets/Hamby252_3DX3P1of2/Br1 Bullet 1-5.x3p"
im115 <- fortify_x3p(read.x3pplus(br115))
qplot(y, x, fill=value, data=im115, geom="tile")
ggsave(file="im115.pdf")
